Variable Circular Plots: Station Placement and the Independence Assumption

### 2014-06-10 presentation/VCPSlides.tex
corrected a few things.
added Text to slides at Claudio's suggestion.

\mode<presentation>
{
	\usetheme{CambridgeUS}
	\setbeamercovered{transparent}
	\setbeamertemplate{footline}[page number]{}
	\setbeamertemplate{navigation symbols}{} % remove navigation symbols
	\setbeamercolor{palette tertiary}{fg=white, bg=OSUdkbrn}
	\setbeamercolor{title}{fg=OSUdkbrn}
	\setbeamercolor{frametitle}{fg=OSUdkbrn}
	\setbeamertemplate{itemize items}[square]
	\setbeamercolor*{item}{fg=OSUdkbrn}
%	
	\setbeameroption{show only notes} % ----------------------- NOTES TOGGLE ---------------------
%
}

\title{Variable Circular Plots: Station Placement and the Independence Assumption}
\subtitle{Master's Research Project}
\author{Matt Edwards\\ Advisor: Claudio Fuentes}
\date{June 11, 2014}

@@

\begin{frame}{Distance Sampling}
	\begin{itemize}
	\item Population Density Estimation
	\item[]
	\item Used often in Ecological Sciences
	\item[]
	\item Began with roadside surveys in early 1900s
	\item[]
	\item Theory developed through mid-1900s

@@

\begin{frame}{Distance Sampling: History}
	\begin{itemize}
	\item Emlen---1971
	\item Ramsey, Scott---1979, 1980 Papers
	\item Burnham, Anderson, and Jeffrey L. Laake---1980 Monograph
	\item Buckland et. al. 1993, 2001---text
	\item Continued Development into 2000s
	\begin{itemize}
	\item Combined with Mark-Recapture Methods
	\item Extended for use with underwater acoustics for estimates of krill populations 
	\item Combined with camera traps to estimate populations
	\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}{Line Vs. Point Transects}
	\begin{itemize}
	\item Line transects are walked
	\begin{itemize}
		\item Distances perpendicular to transect are recorded, as projected on ground
	\end{itemize}
	\item[]
	\item Point transects: observer(s) stand at station, observe everything within 360\textdegree 
		\begin{itemize}
		\item Alternately: Variable Circular Plots (VCP)
		\item Allow ``cooling'' period
		\item Safer for observer
		\item Straight line distance from Observer is recorded, as projected on ground
		\end{itemize}
	\item[]		
	\item Observations can be from visual sightings, auditory clues, or a combination
	\end{itemize}
\end{frame}

\begin{frame}{Detection Curve: $g(r)$}
	\begin{figure}
		\centering
		\includegraphics[width=\textwidth,height=0.80\textheight,keepaspectratio=true]{../images/detectionCurve.pdf}
	\end{figure}
	\note{
		\begin{itemize}
		\item Perfect Detectability Near to Observer, dropping off. The ``shoulder''
		\item $g(r)$ = probability of detecting an object, given it is at distance $r$
		\item scaled so $g(0) = 1$
		\end{itemize}
	}
\end{frame}

@@

@@

\begin{frame}{Collared Kingfisher Observation Data}

\begin{figure}
	\includegraphics[width=\textwidth]{../images/histogram_dist_20m.pdf}
	\label{fig:82dist}
\end{figure}

@@

\begin{frame}{Research Question}
Do overlapping observation areas violate any underlying independence assumptions?\\
\vspace{1cm}Will it make a difference in our final population density estimates if a bird is observed from more than one station?
\end{frame}

\begin{frame}{VCP Indepencence}
	\begin{itemize}
	\item \textcite{ramsey1979,buckland1987,thompson2012} discuss assumption that VCPs are randomly placed.
	\begin{itemize}
	\item Implicit, but not explicit, possibility of overlap
	\end{itemize}
	\item[]
	\item \textcite{reynolds1980} state the possibility of observing the same bird from more than one station should be avoided.
	\item[]
	\item \textcite{buckland2001} states ``Transects are normally spaced at a sufficient distance to avoid detecting an object from two neighboring transects, although this is not usually critical unless sampling a line changes the animal distribution at neighboring, as yet un-sampled lines.''
	\end{itemize}

@@

\begin{frame}{Transect Layouts}
1 unit on graph = 1 km
	\begin{columns}
		\begin{column}{0.48\textwidth}
			\includegraphics[width=\textwidth]{../images/slides-layoutT2.pdf}
		\end{column}
		\begin{column}{0.48\textwidth}
			\includegraphics[width=\textwidth]{../images/slides-layoutT1.pdf}
		\end{column}
	\end{columns}

@@

\begin{frame}{Structured and Random Layouts}
1 unit on graph = 1 km
	\begin{columns}
		\begin{column}{0.48\textwidth}
			\includegraphics[width=\textwidth]{../images/slides-layoutS.pdf}
		\end{column}
		\begin{column}{0.48\textwidth}
			\includegraphics[width=\textwidth]{../images/slides-layoutR.pdf}
		\end{column}
	\end{columns}

@@

\begin{frame}{Detection Curve: Ideal}
	\begin{figure}
		\centering
		\includegraphics[height=.80\textheight]{../images/detectionCurveScaled.pdf}
	\end{figure}
		\note{
			\begin{itemize}
			\item A halfnormal curve, scaled so that $g(0.5)~0$ and $g(0)=1$
			\item used FDRTOOL package in R.
			\end{itemize}	
		}
\end{frame}

\begin{frame}{Detection Curve: Empirical}
	\begin{figure}
		\centering
		\includegraphics[width=\textwidth]{../images/loess.pdf}
	\end{figure}

@@

\begin{frame}{Movement}
	Three Movement Options:
	\begin{itemize}
	\item No Movement: Objects stayed at origin point
	\item[]
	\item Temporary Movement: Objects would shift away from observer, but shift back to origin after observer ``left''
	\item[]
	\item Compounded Movement: Objects would shift away from observer, would remain at new point after observer moved. (Movement could compound if object was within movement radius for more than one VCP)
	\end{itemize}

@@

\begin{frame}{Empirical vs. Half-Normal}
	\begin{figure}
		\centering
		\includegraphics[height=.80\textheight]{../images/Emp_Vs_Hnorm_1-2.pdf}
	\end{figure}
	\note{
		\begin{itemize}
		\item 1000 Simulations. Each object layout was analyzed with the 6 combinations represented in the graph
		\item Density estimates done using the kernel method with a normal kernel \parencite{quang1993}
		\item Estimates for Empirical detection function biased low.
		\item Estimates using half-normal detection function biased low, but not as bad.
		\end{itemize}	
	}

@@

\begin{frame}{Empirical vs. Half-Normal}{Centers and Spread}
\begin{table}
	\begin{tabular}{ r r |r r| r r r}
		$g(x)$      & Layout     & Mean  & Std Dev & 25th  & Median & 75th  \\ \hline\hline
		Empirical   & Random     & 14.47 & 3.37    & 12.08 & 14.38  & 16.73 \\
		Empirical   & Structured & 14.49 & 3.15    & 12.27 & 14.47  & 16.59 \\
		Empirical   & Transect   & 14.26 & 3.66    & 11.65 & 14.14  & 16.80 \\ \hline
		Half-normal & Random     & 17.90 & 4.57    & 14.67 & 17.86  & 20.88 \\
		Half-normal & Structured & 18.03 & 4.16    & 15.05 & 17.91  & 20.82 \\
		Half-normal & Transect   & 17.80 & 4.64    & 14.52 & 17.44  & 20.78
	\end{tabular}
\end{table}

@@

@@

\begin{frame}{Movement Results}
	\begin{figure}
		\centering
		\includegraphics[height=.80\textheight]{../images/MovementSim2.pdf}
	\end{figure}
	\note{
		\begin{itemize}
		\item 1000 Simulations. Again, each object layout was analyzed with the 9 combinations represented in the graph
		\item Density estimates done using the kernel method with a normal kernel \parencite{quang1993}
		\item Again, layout does not seem to play as large of a part as the other factor.
		\item All were run with half-normal detectability function
		\end{itemize}	
	}
\end{frame}

\begin{frame}{Movement Results}{Centers \& Spread}
	\begin{table}

		\begin{tabular}{ r r| r r| r r r}
			Movement  & Layout     & Mean  & Std Dev & 25th  & Median & 75th  \\ \hline\hline
			None      & Random     & 17.86 & 4.28    & 15.03 & 17.64  & 20.65 \\
			None      & Structured & 18.01 & 4.51    & 14.95 & 17.62  & 20.94 \\
			None      & Transect   & 17.90 & 4.78    & 14.74 & 17.67  & 20.95 \\ \hline
			Compounded & Random     & 11.86 & 3.42    & 9.58  & 11.61  & 14.09 \\
			Compounded & Structured & 11.90 & 3.65    & 9.37  & 11.67  & 14.08 \\
			Compounded & Transect   & 12.42 & 3.72    & 9.93  & 12.17  & 14.79 \\ \hline
			Temporary & Random     & 11.76 & 3.57    & 9.22  & 11.75  & 14.02 \\
			Temporary & Structured & 11.74 & 3.48    & 9.37  & 11.56  & 13.85 \\
			Temporary & Transect   & 11.75 & 3.57    & 9.24  & 11.72  & 14.20
		\end{tabular}

	\end{table}
	\note{
	\begin{itemize}
	\item Reinforced histograms: results consistent within movement type, regardless of layout type
	\item No Movement is consistent with what was observed in initial simulation
	\item 
	\end{itemize}
	}
\end{frame}

\begin{frame}{Movement Results}{True Density Capture}
	\begin{table}

@@

	\note{
	\begin{itemize}
	\item Movement type does not appear to play a large part in changing the bias.
	\item We capture the true density about 59\% of the time, regardless of movement type.
	\end{itemize}
	}
\end{frame}

@@

\begin{frame}{Movement Testing}
	\begin{figure}
		\centering
		\includegraphics[width=\textwidth]{../images/movementTest.pdf}
	\end{figure}
\end{frame}

\begin{frame}{Change in Area}

	\begin{columns}
		\begin{column}{0.48\textwidth}
		\includegraphics[width=\textwidth]{../images/slides-LTr.pdf}
		\end{column}
		\begin{column}{0.48\textwidth}
		\includegraphics[width=\textwidth]{../images/slides-VCPr.pdf}
		\end{column}
	\end{columns}

@@

\begin{frame}{Circles vs. Rectangles}{Area and Expected Observation Counts}
	\begin{columns}
		\begin{column}{0.48\textwidth}
		\includegraphics[width=\textwidth]{../images/rect-circ-area.pdf}
		\end{column}
		\begin{column}{0.48\textwidth}
		\includegraphics[width=\textwidth]{../images/rect-circ-detection.pdf}
		\end{column}
	\end{columns}
	\begin{center}
	\par Solid line is Line Transect, Dashed line is VCP
	\end{center}

@@

\begin{frame}{Conclusion}
	If all else is held equal, VCP layout does not seem to play a large role in the bias of population density estimates using the kernel method described by \textcite{quang1993}.\par
		\vspace{1cm}
	Violations of the expected detection probability curve, or by movement of the objects away from the observer play a greater role in biasing the resulting estimate.

@@

\begin{frame}{Future Work}
	\begin{itemize}
	\item Explore the possible interaction effect from Compounded Movement and the Transect Layout
	\item[]
	\item Modify simulation functions to return more information to assist diagnostics
	\begin{itemize}
	\item Count of Observed Objects
	\item Observation Distances
	\end{itemize}
	\item[]
	\item Modify using the Empirical data as a detectability function, to account for difference between line and point transects.
	\item[]
	\item Add the option to bias-correct the estimates, to see how well Quang's kernel method adjusts for these variations.
	\end{itemize}
\end{frame}

\begin{frame}{Final Words}
\begin{quote}
``All models are wrong, but some are useful.'' --George E. P. Box
\end{quote}

@@

\section{Additional Data}
\begin{frame}{Object placement Simulation}

	\begin{figure}
		\centering
		\includegraphics[height=.80\textheight]{../images/slides-pointGeneration.pdf}
	\end{figure}
\end{frame}

\begin{frame}{Half-Normal Scaling}
	The half-normal parameter $\theta$ is related to the standard deviation of a standard normal distribution by the relationship: 
	\begin{center}
	$\theta = \dfrac{\sqrt{\pi /2}}{\sigma}$
	\end{center}

	If we estimate $\sigma$ by $w/3.5$ (with $w$ being the maximum distance at which we might observe an object, and 3.5 being the standard deviation point where $P(X > 3.5) < 0.001$) then $\theta$ is:
	\begin{center}
	$\sigma = \dfrac{w}{3.5} = 0.1429$\\
	\vspace{0.5cm}
	$\theta = \dfrac{\sqrt{\pi /2}}{0.1429}=8.7732$
	\end{center}
\end{frame}

\begin{frame}{Half-Normal Scaling}
	For a half-normal with parameter $\theta=8.7732$, $f(0)=5.5852$ so to scale the value to 1:
	\begin{center}
	$\delta_{HN} = \dfrac{1}{5.5852} = 0.1790$
	\end{center}

	Half-normal density functions were executed in R with the \texttt{fdrtool} package.
\end{frame}

>>>>

\mode<presentation>
{
	\usetheme{CambridgeUS}
	\setbeamercovered{transparent}
	\setbeamertemplate{footline}[page number]{}
	\setbeamertemplate{navigation symbols}{} % remove navigation symbols
	\setbeamercolor{palette tertiary}{fg=white, bg=OSUdkbrn}
	\setbeamercolor{title}{fg=OSUdkbrn}
	\setbeamercolor{frametitle}{fg=OSUdkbrn}
	\setbeamertemplate{itemize items}[square]
	\setbeamercolor*{item}{fg=OSUdkbrn}
%	
%	\setbeameroption{show only notes} % ----------------------- NOTES TOGGLE ---------------------
%
}

\title{Variable Circular Plots: Station Placement and the Independence Assumption}
\subtitle{Master's Research Project}
\author{Matt Edwards}
\date{June 11, 2014}

@@

\begin{frame}{Distance Sampling}
Distance sampling is a method of population density estimation that considers the probably of observing the object of interest at the distance at which it was seen.

	\begin{itemize}
	\item Used often in Ecological Sciences
	\item[]
	\item Began with roadside surveys in early 1900s
	\item[]
	\item Theory developed through mid-1900s

@@

\begin{frame}{Distance Sampling: History}
A selection of relevant papers:
	\begin{itemize}
	\item Emlen---1971
	\item Ramsey, Scott---1979, 1980 Papers
	\item Burnham, Anderson, and Jeffrey L. Laake---1980 Monograph
	\item Buckland et. al. 1993, 2001---text
	\item Continued Development into 2000s
	\begin{itemize}
	\item Combined with Mark-Recapture Methods
	\item Extended for use with underwater acoustics for estimates of krill populations 
	\item Combined with camera traps to estimate populations
	\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}{Line vs Point Transects}
	\begin{itemize}
	\item Line transects are walked
	\begin{itemize}
		\item Distances perpendicular to transect are recorded, as projected on ground
	\end{itemize}
	\item[]
	\item Point transects: observer(s) stand at station, observe everything within 360\textdegree 
		\begin{itemize}
		\item Alternately: Variable Circular Plots (VCP)
		\item Allow ``cooling'' period
		\item Safer for observer
		\item Straight line distance from Observer is recorded, as projected on ground
		\end{itemize}
	\item[]		
	\item Both: Observations can be from visual sightings, auditory clues, or a combination
	\end{itemize}
\end{frame}

\begin{frame}{Transect Examples}

	\begin{columns}
		\begin{column}{0.48\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../images/slides-LTr.pdf}\\
		Line Transect
		\end{column}
		\begin{column}{0.48\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../images/slides-VCPr.pdf}\\
		VCP/Point Transect
		\end{column}
	\end{columns}

\begin{frame}{Detection Curve: $g(r)$}
The probability of detecting an object, give it is at distance $r$.
	\begin{figure}
		\centering
		\includegraphics[width=\textwidth,height=0.80\textheight,keepaspectratio=true]{../images/detectionCurve.pdf}
	\end{figure}
	\note{
		\begin{itemize}
		\item Perfect Detectability Near to Observer, dropping off. The ``shoulder''
		\item $g(r)$ = probability of detecting an object, given it is at distance $r$
		\item scaled so $g(0) = 1$
		\end{itemize}
	}
\end{frame}

@@

	\begin{itemize}
	\item $\hat{D}$: Estimated Population Density
	\item $n$: number of objects observed
	\item $Area$: The area surveyed
	\item $g(r)$: $P(\mbox{observing object}|\mbox{distance }r)$
	\end{itemize}

@@

\begin{frame}{Collared Kingfisher Observation Data}
Aggregated empirical observation distances from 1982 study.
\begin{figure}
	\includegraphics[width=\textwidth]{../images/histogram_dist_20m.pdf}
	\label{fig:82dist}
\end{figure}

@@

\begin{frame}{Research Question}
\Large
{\bfseries Do overlapping observation areas violate any underlying independence assumptions?}\\
\vspace{1cm}
{\bfseries Will it make a difference in our final population density estimates if a bird is observed from more than one station?}
\end{frame}

\begin{frame}{VCP Indepencence}
	VCP Analysis assumes sightings of animals are independent events.
	\begin{itemize}
	\item[]
	\item \textcite{ramsey1979,buckland1987,thompson2012} discuss assumption that VCPs are randomly placed.
	\begin{itemize}
	\item Implicit, but not explicit, possibility of overlap
	\end{itemize}
	\item[]
	\item \textcite{reynolds1980} state the possibility of observing the same bird from more than one station should be avoided.
	\item[]
	\item \textcite{buckland2001} states ``Transects are normally spaced at a sufficient distance to avoid detecting an object from two neighboring transects, although this is not usually critical unless sampling a line changes the animal distribution at neighboring, as yet un-sampled lines.''
	\end{itemize}

@@

\begin{frame}{Transect Layouts}
Examples of two random Transect layouts.\\
1 unit on graph = 1 km
	\begin{columns}
		\begin{column}{0.48\textwidth}
			\includegraphics[width=\textwidth]{../images/slides-layoutT2.pdf}
		\end{column}
		\begin{column}{0.48\textwidth}
			\includegraphics[width=\textwidth]{../images/slides-layoutT1.pdf}
		\end{column}
	\end{columns}

@@

\begin{frame}{Structured and Random Layouts}
Examples of Structured and Random layouts.\\
1 unit on graph = 1 km
	\begin{columns}
		\begin{column}{0.48\textwidth}
			\includegraphics[width=\textwidth]{../images/slides-layoutS.pdf}
		\end{column}
		\begin{column}{0.48\textwidth}
			\includegraphics[width=\textwidth]{../images/slides-layoutR.pdf}
		\end{column}
	\end{columns}

@@

\begin{frame}{Detection Curve: Ideal}
``Ideal'' detection probability curve, maximum observation distance set to 0.5 unit (500 m) distance, and scaled so $g(0)=1$
	\begin{figure}
		\centering
		\includegraphics[height=.75\textheight]{../images/detectionCurveScaled.pdf}
	\end{figure}
		\note{
			\begin{itemize}
			\item A halfnormal curve, scaled so that $g(0.5)~0$ and $g(0)=1$
			\item used FDRTOOL package in R.
			\end{itemize}	
		}
\end{frame}

\begin{frame}{Detection Curve: Empirical}
Detection probability curve from empirical data, shown unscaled.
	\begin{figure}
		\centering
		\includegraphics[width=\textwidth]{../images/loess.pdf}
	\end{figure}

@@

\begin{frame}{Movement}
	The histogram of observed distances shows evidence of movement, so it was considered as an option for simulation.\\
	\vspace{0.33cm}
	Three Movement Options:
	\begin{itemize}
	\item No Movement: Objects stayed at origin point
	\item[]
	\item Temporary Movement: Objects would shift away from observer, but shift back to origin after observer ``left''
	\item[]
	\item Compounded Movement: Objects would shift away from observer, would remain at new point after observer moved. (Movement could compound if object was within movement radius for more than one VCP)
	\end{itemize}

@@

\begin{frame}{Empirical vs. Half-Normal}
	\small
	1000 simulations, comparing Empirical vs Half-Normal detection probability, no movement, 
	\begin{figure}
		\centering
		\includegraphics[height=.80\textheight]{../images/Emp_Vs_Hnorm_1-2.pdf}
	\end{figure}
	\note{
		\begin{itemize}
		\item 1000 Simulations. Each object layout was analyzed with the 6 combinations represented in the graph
		\item Density estimates done using the kernel method with a normal kernel \parencite{quang1993}
		\item Estimates for Empirical detection function biased low.
		\item Estimates using half-normal detection function biased low, but not as bad.
		\end{itemize}	
	}

@@

\begin{frame}{Empirical vs. Half-Normal}{Centers and Spread}

\begin{table}
	\begin{tabular}{ r r |r r| r r r}
		$g(x)$      & Layout     & Mean  & Std Dev & 25th  & Median & 75th  \\ \hline\hline
		Empirical   & Random     & 14.47 & 3.37    & 12.08 & 14.38  & 16.73 \\
		Empirical   & Structured & 14.49 & 3.15    & 12.27 & 14.47  & 16.59 \\
		Empirical   & Transect   & 14.26 & 3.66    & 11.65 & 14.14  & 16.80 \\ \hline
		Half-normal & Random     & 17.90 & 4.57    & 14.67 & 17.86  & 20.88 \\
		Half-normal & Structured & 18.03 & 4.16    & 15.05 & 17.91  & 20.82 \\
		Half-normal & Transect   & 17.80 & 4.64    & 14.52 & 17.44  & 20.78
	\end{tabular}
\end{table}
\small
Comparing measures of centers and spread, 1000 simulations, no movement.

@@

\small
Comparing rates of capture for true object density, 1000 simulations, no movement.

@@

\begin{frame}{Movement Results}
\small
	1000 simulations, comparing effect of movement types. Half-normal detection probability used for all.
	\begin{figure}
		\centering
		\includegraphics[height=.80\textheight]{../images/MovementSim2.pdf}
	\end{figure}
	\note{
		\begin{itemize}
		\item 1000 Simulations. Again, each object layout was analyzed with the 9 combinations represented in the graph
		\item Density estimates done using the kernel method with a normal kernel \parencite{quang1993}
		\item Again, layout does not seem to play as large of a part as the other factor.
		\item All were run with half-normal detectability function
		\end{itemize}	
	}
\end{frame}

\begin{frame}{Movement Results}{Centers \& Spread}

	\begin{table}

		\begin{tabular}{ r r| r r| r r r}
			Movement  & Layout     & Mean  & Std Dev & 25th  & Median & 75th  \\ \hline\hline
			None      & Random     & 17.86 & 4.28    & 15.03 & 17.64  & 20.65 \\
			None      & Structured & 18.01 & 4.51    & 14.95 & 17.62  & 20.94 \\
			None      & Transect   & 17.90 & 4.78    & 14.74 & 17.67  & 20.95 \\ \hline
			Compounded & Random     & 11.86 & 3.42    & 9.58  & 11.61  & 14.09 \\
			Compounded & Structured & 11.90 & 3.65    & 9.37  & 11.67  & 14.08 \\
			Compounded & Transect   & 12.42 & 3.72    & 9.93  & 12.17  & 14.79 \\ \hline
			Temporary & Random     & 11.76 & 3.57    & 9.22  & 11.75  & 14.02 \\
			Temporary & Structured & 11.74 & 3.48    & 9.37  & 11.56  & 13.85 \\
			Temporary & Transect   & 11.75 & 3.57    & 9.24  & 11.72  & 14.20
		\end{tabular}
	\small
	Comparing measures of center and spread for different movement types. 1000 simulations, half-normal detection probability used for all.
	\end{table}
	\note{
	\begin{itemize}
	\item Reinforced histograms: results consistent within movement type, regardless of layout type
	\item No Movement is consistent with what was observed in initial simulation
	\item 
	\end{itemize}
	}
\end{frame}

\begin{frame}{Movement Results}{True Density Capture}

	\begin{table}

@@

	\end{table}
	\small
	Comparing capture of true object density for different movement types. 1000 simulations, half-normal detection probability used for all.
	\note{
	\begin{itemize}
	\item Movement type does not appear to play a large part in changing the bias.
	\item We capture the true density about 59\% of the time, regardless of movement type.
	\end{itemize}
	}
\end{frame}

@@

\begin{frame}{Movement Testing}
Results of movement code test (left) vs no movement ``baseline'' (right).
	\begin{figure}
		\centering
		\includegraphics[width=\textwidth]{../images/movementTest.pdf}
	\end{figure}
\end{frame}

\begin{frame}{Change in Area}
	Area increase from 1 unit expansion in Line Transect does not equal the area from the same increase in a VCP.
	\begin{columns}
		\begin{column}{0.48\textwidth}
		\includegraphics[width=\textwidth]{../images/slides-LTr.pdf}
		\end{column}
		\begin{column}{0.48\textwidth}
		\includegraphics[width=\textwidth]{../images/slides-VCPr.pdf}
		\end{column}
	\end{columns}

@@

\begin{frame}{Circles vs. Rectangles}{Area and Expected Observation Counts}
	\begin{columns}
		\begin{column}{0.48\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../images/rect-circ-area.pdf}\\
		\small
		Increase in Area
		\end{column}
		\begin{column}{0.48\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../images/rect-circ-detection.pdf}\\
		\small
		Expected number of observations, given distance.
		\end{column}
	\end{columns}
	\begin{center}
	\par Solid line is Line Transect, Dashed line is VCP
	\end{center}

@@

\begin{frame}{Conclusion}
There are two primary conclusions:\\
\vspace{0.5cm}
	\begin{itemize}
	\item If all else is held equal, VCP layout does not seem to play a large role in the bias of population density estimates using the kernel method described by \textcite{quang1993}.
	\item[]
	\item Violations of the expected detection probability curve, or by movement of the objects away from the observer play a greater role in biasing the resulting estimate.
	\end{itemize}

@@

\begin{frame}{Future Work}
Some possible areas for future research:

	\begin{itemize}
	\item Explore the possible interaction effect from Compounded Movement and the Transect Layout
	\item[]
	\item Modify simulation functions to return more information to assist diagnostics
	\begin{itemize}
	\item Count of Observed Objects
	\item Observation Distances
	\end{itemize}
	\item[]
	\item Modify using the Empirical data as a detectability function, to account for difference between line and point transects.
	\end{itemize}
\end{frame}

\begin{frame}{Future Work}
	\begin{itemize}
	\item Add the option to bias-correct the estimates, to see how well Quang's kernel method adjusts for these variations.
	\item[]
	\item Address analyzing transects as clusters, since observations on a transect are likely to be related.

\begin{frame}{Final Words}
	\begin{quote}
	``All models are wrong, but some are useful.'' --George E. P. Box
	\end{quote}
\end{frame}

	\begin{frame}{Acknowledgements}
	Micronesian Survey Data courtesy of Fred Ramsey\\
	\vspace{1cm}
	Masters Committee:
	\begin{itemize}
	\item[] Claudio Fuentes, Advisor
	\item[] Alix Gitelman, Committee Member
	\item[] Charlotte Wickham, Committee Member
	\end{itemize}
\end{frame}

@@
